One-stage point transect distance sampling using iterated integrated nested Laplace approximations

### 2019-12-10 paper-v2.tex
update study area plot

\begin{figure}
	\centering
	\includegraphics[scale=0.5]{figures/2002studyareapoints_pt}
	\caption{Study area (light blue) showing the 2002 survey points (black dots) in Hakalau Forest National Wildlife Refuge, \hawaii{} Island.}
	\label{fig:2002studyareapointspt}
\end{figure}

>>>>

\begin{figure}
	\centering
	\includegraphics[scale=0.5]{figures/study_area_design.png}
	\caption{Study area showing the 2002 survey points (black dots) in Hakalau Forest National Wildlife Refuge, \hawaii{} Island.}
	\label{fig:2002studyareapointspt}
\end{figure}
